Lyman-$\alpha$ photons through rotating outflows

### 2018-03-29 paper/paper.tex
edit

>>>>

Figure \ref{fig:standard_deviation} summarizes the results for STD.
Each panel shows the STD as a function of \vrot.
The black triangles correspond to the full RT solution and the line to
the Doppler Shift approximation. 
The optical depth increases from top to bottom and the outflow
velocity from left to right.
This quantitative plot confirms that the line width increases with
rotational velocity, all else being equal.
The Doppler Shift sucessfuly reproduces this trend, albeit a consistent
underestimation of the RT values; this underestimation has as an upper
bound of $\sim 7\%$, $3\%$ and $\sim 2\%$ for $\tauh=10^5$, $10^6$ and
$10^7$, respectively.
Tee Doppler Shift approximation also improves as the outflow velocity
decreases.

The mismatch between RT and DS decreases for higher
